---
title: "CXOwt"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CXOwt}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warnings = FALSE, 
  messages = FALSE, 
  prompt = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CXOwt 

This R package was is code to implement weighted conditional logistic regression described  [here](https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/s12874-021-01408-5). 

## Installation

`CXOwt` is still under development. You can install the latest version from [GitHub](https://github.com/) with:

```{r install, results = "hide", eval = FALSE}
# install.packages("remotes")
remotes::install_github("lan-k/CXOwt")
```

## Using the package

`CXOwt` contains functions for both case-crossover and case-time-control designs. There are 2 example dataframes, `cases` and `casetimecontrols`.

`CXO_wt_boot()` is the version for case-crossover studies, `CXO_tc_wt_boot()` for case-time-control studies. Both return the weighted Odds Ratio estimate and bootstrapped 95% confidence intervals.

```{r example1, eval=F}
library(CXOwt)
#case-crossover
data(cases)
cfit.b <- CXO_wt_boot(data=cases, exposure = ex, event = Event, Id=Id, B=200) 
summary(cfit.b)
#case-time-control
data(casetimecontrols)
ctcfit.b <- CXO_tc_wt_boot(data=casetimecontrols, exposure = ex, event = Event, Id=Id, B = 200) 
summary(ctcfit.b)
```


Alternatively, you can return the weighted conditional logistic regression objects without bootstrapping:

```{r example2, eval=F}
#case-crossover
cfit <- CXO_wt(cases, exposure = ex, event = Event, Id=Id)  
summary(cfit)
#case-time-control
ctcfit <- CXO_tc_wt(casetimecontrols, exposure = ex, event = Event, Id=Id)   
summary(ctcfit)
```
